Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-10-12 parts/intro.tex
working on letter2

\begin{itemize}
\item Firstly we have diagnostics based on morphology.
  Section~\ref{sec:morph} and Fig.~\ref{fig:splinput} explain
  this diagnostic in more detail. We consider:
\begin{enumerate}
\item Whether the images are unblended:  Distinct, unblended images are
  an advantage in modelling, although not essential.
\item Whether all images are discernible.  The topography of an
  arrival-time surface, as encoded by a spaghetti diagram, may require
  more images than are visible, in which case the modeller has to
  insert conjectural image positions.
\item Whether the lens is isolated.
\item The image morphology concisely described: double or quads,
  further sub-categorised to indicate the elongation direction of the
  lensing mass.
\end{enumerate}
\item Secondly we have mass models, covered in Section~\ref{sec:massmodels}.
  We assess the following points:
\begin{enumerate}
\setcounter{enumi}{4}
\item Whether the mass map is reasonable (see Fig.~\ref{fig:kappa}).
\item Whether the arrival-time surface and synthetic image are
  plausible. In particular, an unsatisfactory model is flagged when 
  additional images are implied in regions
  where they are not observed (see Figs.~\ref{fig:arriv}, \ref{fig:synth} \ref{fig:encl}).
\end{enumerate}
\item Thirdly, whether the total implied lensing mass determined from
  the lens model is plausible, given the photometry of the lensing
  galaxy.  In this work we define the lensing mass as the sum of all
  mass tiles in the model.  These mass tiles reach out to typically
  twice the radius of the outermost image.
  Section~\ref{sec:stellar-mass} explains how we compare the lensing
  (i.e. total) mass with the stellar mass. Naturally, the lensing
  mass should be somewhere between the stellar mass (lower bound)
  and the total halo mass (upper bound).
\begin{enumerate}
\setcounter{enumi}{6}
\item We then introduce a so-called halo index ($\haloindex$), that
  quantifies how the lensing mass compares with these two
  constraints (see Fig.~\ref{fig:stelmass}).
\end{enumerate}
\end{itemize}

>>>>

\begin{itemize}
\item Firstly we have diagnostics based on morphology.
  Section~\ref{sec:morph} and Fig.~\ref{fig:splinput} explain
  this diagnostic in more detail. We consider:
\begin{enumerate}
\item Whether the images are unblended:  Distinct, unblended images are
  an advantage in modelling, although not essential.
\item Whether all images are discernible.  The topography of an
  arrival-time surface, as encoded by a spaghetti diagram, may require
  more images than are visible, in which case the modeller has to
  insert conjectural image positions.
\item Whether the lens is isolated.
\item The image morphology concisely described: double or quads,
  further sub-categorised to indicate the elongation direction of the
  lensing mass.
\end{enumerate}
\item Secondly we have mass models, covered in Section~\ref{sec:massmodels}.
  We assess the following points:
\begin{enumerate}
\setcounter{enumi}{4}
\item Whether the mass map is reasonable (see Fig.~\ref{fig:kappa}).
\item Whether the arrival-time surface and synthetic image are
  plausible. In particular, an unsatisfactory model is flagged when 
  additional images are implied in regions
  where they are not observed (see Figs.~\ref{fig:arriv}, \ref{fig:synth} \ref{fig:encl}).
\end{enumerate}
\item Thirdly, whether the total implied lensing mass determined from
  the lens model is plausible, given the photometry of the lensing
  galaxy.  In this work we define the lensing mass as the sum of all
  mass tiles in the model.  These mass tiles reach out to typically
  twice the radius of the outermost image.
  We note that even though this definition of the lensing mass encloses
  most of the total galaxy mass, since the halos extend well beyond this, it
  creates a bias toward low lensing masses, compared to their total mass.
  One solution would be to extrapolate as done in \citet{2012MNRAS.424..104L},
  but this has not been tried yet.
  Section~\ref{sec:stellar-mass} explains how we compare the lensing
  (i.e. total) mass with the stellar mass. Naturally, the lensing
  mass should be somewhere between the stellar mass (lower bound)
  and the total halo mass (upper bound).
\begin{enumerate}
\setcounter{enumi}{6}
\item We then introduce a so-called halo index ($\haloindex$), that
  quantifies how the lensing mass compares with these two
  constraints (see Fig.~\ref{fig:stelmass}).
\end{enumerate}
\end{itemize}
